Accounting for uncertainty in simulating greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-13 Manuscript_figures.Rmd
corresponds to the first draft of methods

@@

```{r, warning=FALSE, message=FALSE,fig.dim = c(8, 4)}

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 4)}

@@

all_farms_intensity<-ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") + theme_bw() +
    xlab(expression(Emissions~intensity~(kg~CO[2]*'-eq'~kg^-1))) + ggtitle("b) Emissions intensity")

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 6)}
normal_milk_yield<-which(GHG_simulation_scenarios$y$pc_milk_yield>500)

@@

dens1 <- ggplot(dairy_households$y, aes(x = pc_milk_yield)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(fill="lightskyblue3") + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, alpha=0) + 
  theme_void() + 
  theme(legend.position = "none")

@@

densi<-ggplot(dairy_households$y, aes(x = pc_milk_yield, y = CO2eq_per_milk)) +
  stat_density_2d(
    geom = "raster",
    aes(fill = after_stat(density)),
    contour = FALSE
    ) +
  scale_fill_viridis_c() + 
  labs(y=expression(Emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Milk~yield~per~capita~(kg~head^{-1}~year^{-1}))) +
  theme_bw()

dens1 + plot_spacer() + plot_spacer() + plot1 + dens2 + densi + 
  plot_layout(ncol = 3, nrow = 2, widths = c(4, 1), heights = c(1, 4))

@@

```{r varkernelslicerange, message=FALSE, warning=FALSE, fig.dim = c(12, 4)}
slice_2000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)
slice_3000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=3000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

@@

```{r, fig.dim = c(8, 4)}

@@

for (i in 1:(length(milk_yields_to_sample) - 1))
{
  for (j in (i + 1):length(milk_yields_to_sample))
    {decreased_emissions_probability[nrow(decreased_emissions_probability)+1,"Base_yield"]<-milk_yields_to_sample[i]
     decreased_emissions_probability$new_yield[nrow(decreased_emissions_probability)]<-milk_yields_to_sample[j]
     decreased_emissions_probability$probability[nrow(decreased_emissions_probability)] <-
      sum(slices[[i]] > slices[[j]]) / length(slices[[i]])

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~of~'higher-productivity'~farm~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~'lower-productivity'~farm~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") +
  stat_contour(breaks = c(0.9),col="black") + theme_bw()

@@

>>>>

variables_to_update_posnorm<-c(paste0("milk_yield_",4:6),
                             "feed_prod_CO2",
                             "feed_trans_CO2",
                             paste0("live_weight_LW_",1:12),
                             paste0("weight_gain_WG_",1:12),
                             "DE_perc",
                             "perc_crude_protein_diet")

@@

```{r, warning=FALSE, message=FALSE,fig.dim = c(8, 4), fig.cap = "Total farm emissions and emissions intensity for farm number 5 from the farm survey, based on the outputs of a Monte Carlo simulation. The blue bar indicates a point estimate based on the default values recommended by the IPCC"}

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 4), fig.cap = "Total greenhouse gas emissions per farm and emissions intensity across all farms in the farm survey, based on the outputs of a Monte Carlo simulation."}

@@

all_farms_intensity<-ggplot(data=GHG_simulation_scenarios$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") + theme_bw() +
    xlab(expression(Emissions~intensity~(kg~CO[2]*'-eq'~kg^-1))) + ggtitle("b) Emissions intensity")

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 6), fig.cap="Relationship between milk yield per capita and emissions intensity of milk production for farms in Kenya, based on a Monte Carlo simulation. Outputs are shown as a scatter plot (left) and a density surface (right)."}
normal_milk_yield<-which(GHG_simulation_scenarios$y$pc_milk_yield>500)

@@

dens1 <- ggplot(dairy_households$y, aes(x = pc_milk_yield)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(fill="lightskyblue3") + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, alpha=0) + 
  theme_void() + 
  theme(legend.position = "none") + ggtitle("a) Scatter plot of farm-scale data")

@@

densi<-ggplot(dairy_households$y, aes(x = pc_milk_yield, y = CO2eq_per_milk)) +
  stat_density_2d(
    geom = "raster",
    aes(fill = after_stat(density)),
    contour = FALSE
    ) +
  scale_fill_viridis_c() + 
  labs(y=expression(Emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Milk~yield~per~capita~(kg~head^{-1}~year^{-1})),
       fill="Probability \ndensity") +
  theme_bw() + geom_vline(xintercept=c(2000,3000),color=c("#F8766D","#00BFC4"),alpha=.5, lwd=2)

empty<-ggplot() +
    theme_void() +
    ggtitle("b) Interpolated probability density surface")

dens1 + plot_spacer() + empty + plot1 + dens2 + densi + 
  plot_layout(ncol = 3, nrow = 2, widths = c(4, 1), heights = c(1, 4))

@@

```{r varkernelslicerange, message=FALSE, warning=FALSE, fig.dim = c(12, 4), fig.cap="Probability distributions of greenhouse gas emissions intensity at specific levels of milk production per capita. Slices through the emissions intensity density surface are shown for a production level of 2000 kg milk per capita and year (left) and as a comparison between production levels of 2000 and 3000 kg milk per capita and year (right)."}
slice_2000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)
slice_3000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=3000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

@@

```{r, fig.dim = c(8, 4), fig.cap="Probability that farms that differ in per capita milk production also differ in greenhouse gas emissions intensity. The surface, which is based on the outputs of a Monte Carlo simulation, expresses the probability that a farm with higher milk productivity (y-axis) has a lower emissions intensity than a farm with lower milk productivity (x-axis)."}

@@

for (i in 2:(length(milk_yields_to_sample) - 1))
{
  for (j in 1:length(milk_yields_to_sample))
    {decreased_emissions_probability[nrow(decreased_emissions_probability)+1,"Base_yield"]<-milk_yields_to_sample[i]
     decreased_emissions_probability$new_yield[nrow(decreased_emissions_probability)]<-milk_yields_to_sample[j]
     decreased_emissions_probability$probability[nrow(decreased_emissions_probability)] <-
      sum(slices[[i]] > slices[[j]]) / length(slices[[i]])
     decreased_emissions_probability$probability[nrow(decreased_emissions_probability)] <-
      sum(slices[[i]] > sample(slices[[j]], length(slices[[i]]))) / length(slices[[i]])

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability of lower emissions intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(breaks = c(0.9),col="black") + theme_bw()

@@

```{r defining_interventions}
# breed intervention

cows<-Kenyaherds[which(Kenyaherds$animal_type %in% 4:6),]

ggplot(cows, aes(factor(breed),milk_yield)) +
  geom_violin(draw_quantiles=c(0.5),fill="light green") +
  xlab("Breed") + ylab("Milk yield (kg per day)") + theme_bw()

ggsave("figures/Fig_S1_breeds.png", width=7,height=5)

milk_summary<-cbind(aggregate(cows$milk_yield, by=list(cows$breed), FUN=median),table(cows$breed))
milk_summary<-milk_summary[,c(1,4,2)]
colnames(milk_summary)<-c("Breed","n","Median_milk_yield")

milk_summary[,"Intervention_factor"]<-sapply(milk_summary$Median_milk_yield, function(x) min(x/milk_summary$Median_milk_yield[1],1))

live_weights<-aggregate(Kenyaherds$live_weight_LW, by=list(Kenyaherds$animal_type,Kenyaherds$breed), FUN=median)
colnames(live_weights)<-c("animal_type","breed","median_live_weight")
live_weights[,"Intervention_factor"]<-NA
for(i in 1:nrow(live_weights))
  live_weights$Intervention_factor[i]<-live_weights$median_live_weight[i]/
     live_weights$median_live_weight[which(live_weights$animal_type==live_weights$animal_type[i] &                                                                                                            live_weights$breed==1)]

# mature weight should probably be changed, and the code below does this. However, the mature weight is currently the same for all the breeds, so this accomplished nothing.

mature_weights<-aggregate(Kenyaherds$mature_weight_MW, by=list(Kenyaherds$animal_type,Kenyaherds$breed), FUN=median)
colnames(mature_weights)<-c("animal_type","breed","median_mature_weight")
mature_weights[,"Intervention_factor"]<-NA
for(i in 1:nrow(mature_weights))
  mature_weights$Intervention_factor[i]<-mature_weights$median_mature_weight[i]/
     mature_weights$median_mature_weight[which(mature_weights$animal_type==mature_weights$animal_type[i] &                                                                                                            mature_weights$breed==1)]

# same for the weight gain - doesn't depend on the breed at the moment, so all the factors are 1

weight_gains<-aggregate(Kenyaherds$weight_gain_WG, by=list(Kenyaherds$animal_type,Kenyaherds$breed), FUN=median)
colnames(weight_gains)<-c("animal_type","breed","median_weight_gain")
weight_gains[,"Intervention_factor"]<-NA
for(i in 1:nrow(weight_gains))
  weight_gains$Intervention_factor[i]<-weight_gains$median_weight_gain[i]/
     weight_gains$median_weight_gain[which(weight_gains$animal_type==weight_gains$animal_type[i] &                                                                                                            weight_gains$breed==1)]
weight_gains$Intervention_factor[which(weight_gains$median_weight_gain==0)]<-1

farms<-unique(Kenyaherds$QQNO)
breed_intervention<-data.frame(Farm=farms, milk_yield_4=1, milk_yield_5=1, milk_yield_6=1)

Kenyaherds_interventions<-Kenyaherds[,c("QQNO",
                                        "system",
                                        "animal_type",
                                        "breed",
                                        "live_weight_LW",
                                        "mature_weight_MW",
                                        "weight_gain_WG",
                                        "milk_yield",
                                        "dig_energy",
                                        "CP.")]

Kenyaherds_interventions[,"milk_change"]<-0
cows<-which(Kenyaherds_interventions$animal_type %in% 4:6)
Kenyaherds_interventions$milk_change[cows]<- sapply(cows,function(x) 1/milk_summary$Intervention_factor[milk_summary$Breed==Kenyaherds_interventions$breed[x]]  )

milk_change<-aggregate(Kenyaherds_interventions$milk_change[cows], by=list(Kenyaherds_interventions$QQNO[cows], Kenyaherds_interventions$animal_type[cows]), FUN=mean)

Milk_changes_4<-milk_change[which(milk_change$Group.2==4),]
breed_intervention$milk_yield_4[which(breed_intervention$Farm %in% Milk_changes_4[,1])]<-Milk_changes_4[,3]
Milk_changes_5<-milk_change[which(milk_change$Group.2==5),]
breed_intervention$milk_yield_5[which(breed_intervention$Farm %in% Milk_changes_5[,1])]<-Milk_changes_5[,3]
Milk_changes_6<-milk_change[which(milk_change$Group.2==6),]
breed_intervention$milk_yield_6[which(breed_intervention$Farm %in% Milk_changes_6[,1])]<-Milk_changes_6[,3]

for(i in 1:nrow(Kenyaherds_interventions))
  {Kenyaherds_interventions[i,"live_weight_change"]<-
    1/live_weights$Intervention_factor[which(live_weights$animal_type==Kenyaherds_interventions$animal_type[i]&
                                             live_weights$breed==Kenyaherds_interventions$breed[i])]
   Kenyaherds_interventions[i,"weight_gain_change"]<-
     1/weight_gains$Intervention_factor[which(weight_gains$animal_type==Kenyaherds_interventions$animal_type[i]&
                                              weight_gains$breed==Kenyaherds_interventions$breed[i])]
}

live_weight_agg<-aggregate(Kenyaherds_interventions$live_weight_change,
                           by=list(Kenyaherds_interventions$QQNO,Kenyaherds_interventions$animal_type), FUN=mean)
weight_gain_agg<-aggregate(Kenyaherds_interventions$weight_gain_change,
                           by=list(Kenyaherds_interventions$QQNO,Kenyaherds_interventions$animal_type), FUN=mean)

colnames(live_weight_agg)<-c("farm","animal_type","conv_factor")
colnames(weight_gain_agg)<-c("farm","animal_type","conv_factor")

for(i in 1:nrow(live_weight_agg))
  breed_intervention[which(breed_intervention$Farm==live_weight_agg$farm[i]),
                     paste0("live_weight_LW_",live_weight_agg$animal_type[i])]<-
    live_weight_agg$conv_factor[i]

for(i in 1:nrow(weight_gain_agg))
  breed_intervention[which(breed_intervention$Farm==weight_gain_agg$farm[i]),
                     paste0("weight_gain_WG_",weight_gain_agg$animal_type[i])]<-
    weight_gain_agg$conv_factor[i]

breed_intervention[is.na(breed_intervention)]<-1

x_breed_intervention <- GHG_simulation_scenarios$x

adoption_rate <- 1

intervention_adopters<-which(rbinom(nrow(x_breed_intervention),1,adoption_rate)==1)

for (i in 1:nrow(x_breed_intervention))
{
  if (i %in% intervention_adopters) # if farmers adopt, make changes in x file
    x_breed_intervention[i, colnames(breed_intervention)[2:ncol(breed_intervention)]] <-
      x_breed_intervention[i, colnames(breed_intervention)[2:ncol(breed_intervention)]] *
      breed_intervention[which(paste0("Farm_", breed_intervention$Farm) ==
                                 x_breed_intervention$Scenario[i]),
                         2:ncol(breed_intervention)]
}

breed_adopters<-which(!x_breed_intervention$milk_yield_4*x_breed_intervention$N_animal_type_4==GHG_simulation_scenarios$x$milk_yield_4*GHG_simulation_scenarios$x$N_animal_type_4 |
                        !x_breed_intervention$milk_yield_5*x_breed_intervention$N_animal_type_5==GHG_simulation_scenarios$x$milk_yield_5*GHG_simulation_scenarios$x$N_animal_type_5 |
                        !x_breed_intervention$milk_yield_6*x_breed_intervention$N_animal_type_6==GHG_simulation_scenarios$x$milk_yield_6*GHG_simulation_scenarios$x$N_animal_type_6)

## Herd intervention 1 - nobulls

x_nobull_intervention <- GHG_simulation_scenarios$x
nobull_adoption_rate <- 1.0
for (i in 1:nrow(x_nobull_intervention))
{
  if (rbinom(1, 1, nobull_adoption_rate)) # if farmers adopt, make changes in x file
    x_nobull_intervention$N_animal_type_1[i]<-0
}
nobull_adopters<-which(!x_nobull_intervention$N_animal_type_1==GHG_simulation_scenarios$x$N_animal_type_1)

## Herd intervention 2 - lessReplace

x_lessReplace_intervention <- GHG_simulation_scenarios$x
lessReplace_adoption_rate <- 0.23
for (i in 1:nrow(x_lessReplace_intervention))
{
  if (rbinom(1, 1, lessReplace_adoption_rate)) # if farmers adopt, make changes in x file
    x_lessReplace_intervention$N_animal_type_3[i]<-0
}
lessReplace_adopters<-which(!x_lessReplace_intervention$N_animal_type_3==GHG_simulation_scenarios$x$N_animal_type_3)

## Feed intervention 1 - Supplementary legume fodder

x_Calliandra_intervention <- GHG_simulation_scenarios$x
Calliandra_adoption_rate <- 0.3
for (i in 1:nrow(x_Calliandra_intervention))
{
  if (rbinom(1, 1, Calliandra_adoption_rate)) # if farmers adopt, make changes in x file
    {x_Calliandra_intervention$milk_yield_5[i]<-x_Calliandra_intervention$milk_yield_5[i]+0.156
     x_Calliandra_intervention$milk_yield_6[i]<-x_Calliandra_intervention$milk_yield_6[i]+0.156
     x_Calliandra_intervention$DE_perc[i]<-x_Calliandra_intervention$DE_perc[i]+0.14
     x_Calliandra_intervention$perc_crude_protein_diet[i]<-x_Calliandra_intervention$perc_crude_protein_diet[i]-0.07
     x_Calliandra_intervention$feed_prod_CO2[i]<-x_Calliandra_intervention$feed_prod_CO2[i]- (0.726 *
                                        sum(x_Calliandra_intervention[i,paste0("N_animal_type_",1:12)]))

  }
}
Calliandra_adopters<-which(!x_Calliandra_intervention$DE_perc==GHG_simulation_scenarios$x$DE_perc)

## Feed intervention 2 - Balanced diets

x_balance_intervention <- GHG_simulation_scenarios$x
balance_adoption_rate <- 0.14
for (i in 1:nrow(x_balance_intervention))
{
  if (rbinom(1, 1, balance_adoption_rate)) # if farmers adopt, make changes in x file
    {x_balance_intervention$milk_yield_5[i]<-x_balance_intervention$milk_yield_5[i]+0.75
     x_balance_intervention$milk_yield_6[i]<-x_balance_intervention$milk_yield_6[i]+0.75
     x_balance_intervention$feed_prod_CO2[i]<-x_balance_intervention$feed_prod_CO2[i]-(328.5 * 
                    sum(x_balance_intervention[i,paste0("N_animal_type_",1:12)]))
  }
}
balance_adopters<-which(!x_balance_intervention$feed_prod_CO2==GHG_simulation_scenarios$x$feed_prod_CO2)

To run the interventions, we need a function to run the model with a specific set of x values.

```{r}
# single model-run function
run_model<-function(x_data,model)
  {
  varnames<-colnames(x_data)[which(!colnames(x_data)=="Scenario")]
  model_function_ <- function(x) {

    e <- as.list(sapply(X = varnames, FUN = function(i) as.numeric(unlist(x[i]))))
    eval(expr = body(model), envir = e)
  }
  y <- do.call(what = rbind, args = lapply(X = apply(X = x_data, 
                                                     MARGIN = 1, FUN = model_function_), FUN = unlist))
  returnObject <- list(y = data.frame(y), x = data.frame(x_data))
  returnObject$call <- match.call()
  class(returnObject) <- cbind("mcSimulation", class(returnObject))
  return(returnObject)
}
```

```{r, eval=FALSE}
# run model for modified x file
breed_res <- run_model(x_breed_intervention, ghg_emissions)
nobull_res <- run_model(x_nobull_intervention, ghg_emissions)
lessReplace_res <- run_model(x_lessReplace_intervention, ghg_emissions)
Calliandra_res <- run_model(x_Calliandra_intervention, ghg_emissions)
balance_res <- run_model(x_balance_intervention, ghg_emissions)

breed_res$y[,"CO2eq_per_milk"]<-breed_res$y$pc_on_farm/breed_res$y$pc_milk_yield
nobull_res$y[,"CO2eq_per_milk"]<-nobull_res$y$pc_on_farm/nobull_res$y$pc_milk_yield
lessReplace_res$y[,"CO2eq_per_milk"]<-lessReplace_res$y$pc_on_farm/lessReplace_res$y$pc_milk_yield
Calliandra_res$y[,"CO2eq_per_milk"]<-Calliandra_res$y$pc_on_farm/Calliandra_res$y$pc_milk_yield
balance_res$y[,"CO2eq_per_milk"]<-balance_res$y$pc_on_farm/balance_res$y$pc_milk_yield

breed_res$call<-"multi-scenario call"
save_temperature_scenarios(breed_res,"results","Breed_intervention")
nobull_res$call<-"multi-scenario call"
save_temperature_scenarios(nobull_res,"results","Nobull_intervention")
lessReplace_res$call<-"multi-scenario call"
save_temperature_scenarios(lessReplace_res,"results","LessReplace_intervention")
Calliandra_res$call<-"multi-scenario call"
save_temperature_scenarios(Calliandra_res,"results","Calliandra_intervention")
balance_res$call<-"multi-scenario call"
save_temperature_scenarios(balance_res,"results","Balance_intervention")
```

```{r}
breed_res<-load_temperature_scenarios("results","Breed_intervention")
class(breed_res)<-"mcSimulation"
nobull_res<-load_temperature_scenarios("results","Nobull_intervention")
class(nobull_res)<-"mcSimulation"
lessReplace_res<-load_temperature_scenarios("results","LessReplace_intervention")
class(lessReplace_res)<-"mcSimulation"
Calliandra_res<-load_temperature_scenarios("results","Calliandra_intervention")
class(Calliandra_res)<-"mcSimulation"
balance_res<-load_temperature_scenarios("results","Balance_intervention")
class(balance_res)<-"mcSimulation"
```

```{r, fig.dim = c(8, 8), fig.cap="Intervention impact on per capita milk production and greenhouse gas emissions intensity."}

# make data.frame with all intervention results

interventions<-rbind(cbind(breed_res$y[breed_adopters,],
                           intervention="breed",
                           pc_milk_baseline=GHG_simulation_scenarios$y$pc_milk_yield[breed_adopters],
                           CO2_intensity_baseline=GHG_simulation_scenarios$y$CO2eq_per_milk[breed_adopters]),
                     cbind(nobull_res$y[nobull_adopters,],
                           intervention="nobull",
                           pc_milk_baseline=GHG_simulation_scenarios$y$pc_milk_yield[nobull_adopters],
                           CO2_intensity_baseline=GHG_simulation_scenarios$y$CO2eq_per_milk[nobull_adopters]),
                     cbind(lessReplace_res$y[lessReplace_adopters,],
                           intervention="lessReplace",
                           pc_milk_baseline=GHG_simulation_scenarios$y$pc_milk_yield[lessReplace_adopters],
                           CO2_intensity_baseline=GHG_simulation_scenarios$y$CO2eq_per_milk[lessReplace_adopters]),
                     cbind(Calliandra_res$y[Calliandra_adopters,],
                           intervention="Calliandra",
                           pc_milk_baseline=GHG_simulation_scenarios$y$pc_milk_yield[Calliandra_adopters],
                           CO2_intensity_baseline=GHG_simulation_scenarios$y$CO2eq_per_milk[Calliandra_adopters]),
                     cbind(balance_res$y[balance_adopters,],
                           intervention="balance",
                           pc_milk_baseline=GHG_simulation_scenarios$y$pc_milk_yield[balance_adopters],
                           CO2_intensity_baseline=GHG_simulation_scenarios$y$CO2eq_per_milk[balance_adopters]))

interventions[,"milk_change"]<-interventions$pc_milk_yield-interventions$pc_milk_baseline
interventions[,"emissions_intensity_change"]<-interventions$CO2eq_per_milk-interventions$CO2_intensity_baseline
interventions[,"milk_change_relative"]<-(interventions$pc_milk_yield-interventions$pc_milk_baseline)/interventions$pc_milk_baseline*100
interventions[,"emissions_intensity_change_relative"]<-
  (interventions$CO2eq_per_milk-interventions$CO2_intensity_baseline)/interventions$CO2_intensity_baseline*100

interventions_normal_milk<-interventions[which(interventions$pc_milk_yield>500),]

intervention_change <- merge(data.frame(aggregate(interventions_normal_milk$emissions_intensity_change,
                                                  by = list(interventions_normal_milk$intervention),
                                                  FUN = mean)),
                             data.frame(aggregate(interventions_normal_milk$milk_change,
                                                  by = list(interventions_normal_milk$intervention),
                                                  FUN = mean)),
                             by = "Group.1")
colnames(intervention_change) <-
  c("intervention", "emissions_intensity_change", "milk_change")

intervention_colors<-palette.colors(n = 6, palette = "Okabe-Ito", alpha=1, recycle = FALSE)

interventions_scatter<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per capita milk yield (kg)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

interventions_scatter

ggsave("figures/Fig_6a_intervention_impacts.png", width=9,height=6)

```{r, fig.dim = c(8, 8), fig.cap="Intervention impact on relative per capita milk production and relative greenhouse gas emissions intensity, compared to a counterfactual farm with similar properties that does not apply the respective intervention."}

interventions_scatter_relative<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emissions intensity (%)",
       x="Relative change in per capita milk yield (%)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

interventions_scatter_relative

ggsave("figures/Fig_6_intervention_impacts_relative.png", width=9,height=6)

These are noticeable changes, but can they be detected against the random variation that all farms experience? We'll now take another Monte Carlo sample, apply the same interventions to the same farms and evaluate the results again.

```{r, eval=FALSE}

## Run endline Monte Carlo simulation
GHG_simulation_scenarios_time2<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                            scenarios = read.csv("data/farm_scenarios.csv",
                                                                 fileEncoding = "UTF-8-BOM"),
                                            model_function = ghg_emissions,
                                            numberOfModelRuns = 10,
                                            functionSyntax = "plainNames")

GHG_simulation_scenarios_time2$call<-"multi-scenario call"
save_temperature_scenarios(GHG_simulation_scenarios_time2,"results","Endline_no_intervention")

```{r}

GHG_simulation_scenarios_time2<-load_temperature_scenarios("results","Endline_no_intervention")
class(GHG_simulation_scenarios_time2)<-"mcSimulation"

## Produce endline breed scenario
x_breed_intervention_endline <- GHG_simulation_scenarios_time2$x

for (i in breed_adopters)
{x_breed_intervention_endline[i, colnames(breed_intervention)[2:ncol(breed_intervention)]] <-
 x_breed_intervention_endline[i, colnames(breed_intervention)[2:ncol(breed_intervention)]] *
    breed_intervention[which(paste0("Farm_", breed_intervention$Farm) ==
                               x_breed_intervention_endline$Scenario[i]),
                       2:ncol(breed_intervention)]
}

## Herd intervention 1 - nobulls

x_nobull_intervention_endline <- GHG_simulation_scenarios_time2$x
x_nobull_intervention_endline$N_animal_type_1[nobull_adopters]<-0

## Herd intervention 2 - lessReplace

x_lessReplace_intervention_endline <- GHG_simulation_scenarios_time2$x
x_lessReplace_intervention_endline$N_animal_type_3[lessReplace_adopters]<-0

## Feed intervention 1 - Supplementary legume fodder

x_Calliandra_intervention_endline <- GHG_simulation_scenarios_time2$x
for (i in Calliandra_adopters)
{x_Calliandra_intervention_endline$milk_yield_5[i]<-x_Calliandra_intervention_endline$milk_yield_5[i]+0.156
 x_Calliandra_intervention_endline$milk_yield_6[i]<-x_Calliandra_intervention_endline$milk_yield_6[i]+0.156
 x_Calliandra_intervention_endline$DE_perc[i]<-x_Calliandra_intervention_endline$DE_perc[i]+0.14
 x_Calliandra_intervention_endline$perc_crude_protein_diet[i]<-x_Calliandra_intervention_endline$perc_crude_protein_diet[i]-0.07
 x_Calliandra_intervention_endline$feed_prod_CO2[i]<-x_Calliandra_intervention_endline$feed_prod_CO2[i]- (0.726 *
                                        sum(x_Calliandra_intervention_endline[i,paste0("N_animal_type_",1:12)]))
}

## Feed intervention 2 - Balanced diets

x_balance_intervention_endline <- GHG_simulation_scenarios_time2$x
for (i in balance_adopters)
{x_balance_intervention$milk_yield_5[i]<-x_balance_intervention$milk_yield_5[i]+0.75
 x_balance_intervention$milk_yield_6[i]<-x_balance_intervention$milk_yield_6[i]+0.75
 x_balance_intervention$feed_prod_CO2[i]<-x_balance_intervention$feed_prod_CO2[i]-(328.5 * 
                    sum(x_balance_intervention[i,paste0("N_animal_type_",1:12)]))
}

```{r, eval=FALSE}
# run model for modified x file (endline)
breed_end <- run_model(x_breed_intervention_endline, ghg_emissions)
nobull_end <- run_model(x_nobull_intervention_endline, ghg_emissions)
lessReplace_end <- run_model(x_lessReplace_intervention_endline, ghg_emissions)
Calliandra_end <- run_model(x_Calliandra_intervention_endline, ghg_emissions)
balance_end <- run_model(x_balance_intervention_endline, ghg_emissions)

breed_end$y[,"CO2eq_per_milk"]<-breed_end$y$pc_on_farm/breed_end$y$pc_milk_yield
nobull_end$y[,"CO2eq_per_milk"]<-nobull_end$y$pc_on_farm/nobull_end$y$pc_milk_yield
lessReplace_end$y[,"CO2eq_per_milk"]<-lessReplace_end$y$pc_on_farm/lessReplace_end$y$pc_milk_yield
Calliandra_end$y[,"CO2eq_per_milk"]<-Calliandra_end$y$pc_on_farm/Calliandra_end$y$pc_milk_yield
balance_end$y[,"CO2eq_per_milk"]<-balance_end$y$pc_on_farm/balance_end$y$pc_milk_yield

breed_end$call<-"multi-scenario call"
save_temperature_scenarios(breed_end,"results","End_Breed_intervention")
nobull_end$call<-"multi-scenario call"
save_temperature_scenarios(nobull_end,"results","End_Nobull_intervention")
lessReplace_end$call<-"multi-scenario call"
save_temperature_scenarios(lessReplace_end,"results","End_LessReplace_intervention")
Calliandra_end$call<-"multi-scenario call"
save_temperature_scenarios(Calliandra_end,"results","End_Calliandra_intervention")
balance_end$call<-"multi-scenario call"
save_temperature_scenarios(balance_end,"results","End_Balance_intervention")
```

```{r, include=FALSE}
breed_end<-load_temperature_scenarios("results","End_Breed_intervention")
class(breed_end)<-"mcSimulation"
nobull_end<-load_temperature_scenarios("results","End_Nobull_intervention")
class(nobull_end)<-"mcSimulation"
lessReplace_end<-load_temperature_scenarios("results","End_LessReplace_intervention")
class(lessReplace_end)<-"mcSimulation"
Calliandra_end<-load_temperature_scenarios("results","End_Calliandra_intervention")
class(Calliandra_end)<-"mcSimulation"
balance_end<-load_temperature_scenarios("results","End_Balance_intervention")
class(balance_end)<-"mcSimulation"
```

```{r, fig.dim = c(8, 8), fig.cap="Intervention impacts on milk production per capita and greenhouse gas emissions intensity, in comparison to random changes between two evaluation times. The gray dots illustrate random changes that occurred on farms that made no management changes, whereas the colored dots show changes on farms that implemented the respective interventions."}

# make data.frame with all intervention results
